Genetic influence on wood density variation in  white-spruce (*Picea glauca*)

### 2019-11-04 Article_AS.Rmd
Resultats

#3 Results

The model we have developed has made it possible to adjust wood density for each core. A summary of the parameter values obtained of the model fitting process (Eq. 1) can be found in figure 4&5. We observe that the average value of the model parameters differs between Asselin and Saint-Casimir. For the parameters $b_0$ and $b_1$, the average is higher in Saint-Casimir and for parameter $b_2$ it is higher in Asselin. Although there are small differences in the parameters between the two sites, these differences are very small. The fit of the model is therefore similar at both sites.

![Summary graphic of parameters in Asselin.](graph_table/parameter.asselin.png){width=335px; height=330px}

![Summary graphic of parameters in Saint-Casimir.](graph_table/parameters.casimir.png){width=335px; height=330px}

![Pith-to-bark radial pattern of breast height density by ring. Fine lines show densities for individual stands of the samples for the Asselin site. The bold lines shows the density predicted by Model.](graph_table/Density_asselin.png){width=330px; height=330px}

![Pith-to-bark radial pattern of breast height density by ring. Fine lines show densities for individual stands of the samples for the Saint-Casimir site.The bold lines shows the density predicted by Model.](graph_table/Density_casimir.png){width=330px; height=330px}

@@

@@

<!--
```{r aa, echo=FALSE}
data <- readr::read_csv("data/Tableau_resume_indice d'uniformite.csv")
knitr::kable(data)
```
-->

![Summary graphic of index V per site.](graph_table/indexV.png){width=335px; height=330px}

@@

|Rank correlation  |Rho  |P-value |
|:-----------------|----:|-------:|
|Density residus   | 0.57|8.7^-09^|
|Index V           | 0.08|0.43    |
|$b_0$             | 0.70|2.2^-16^|
|$b_1$             | 0.80|2.2^-16^|
|$b_2$             | 0.60|2.2^-16^|
Table: Sperman’s Rang correlation

@@

![Abstract of the heritability ($hi^2$) of the density, the ring width, parameters $b_0$, $b_1$, $b_2$, index V and standard error per site.](graph_table/heritability.png){width=335px; height=330px}

>>>>

# 3 Results

## Mean density per ring and prediction curve of the model

@@

![Pith-to-bark radial patern of the density measured from the cores taken at breast height by ring. A) Density for the site of Asselin and B) Density for the site of Saint-Casimir. The lines indicate densities for individual stands of samples. The bold lines indicate the density predicted by the adjusted model for all trees.](graph_table/Density.pdf)

|Sites             |    N|$R^2$ Adjusted|       E|E   |E%  |
|:-----------------|----:|-------------:|-------:|---:|---:|
|Asselin           | 1035|0.49          |0.000008|58.6|0.15|
|Saint-Casimir     | 1162|0.49          |0.00007 |48.1|0.13|

The fit of the model we developed allowed us to take into account the density profile of each individual tree. A summary of the parameter values obtained of the model fitting process (Eq. 1) can be found in figure 4&5. We observe that the average value of the model parameters differs between Asselin and Saint-Casimir. For the parameters $b_0$ and $b_1$, the average is higher in Saint-Casimir and for parameter $b_2$ it is higher in Asselin. Although there are small differences in the parameters between the two sites, these differences are very small. The fit of the model is therefore similar at both sites.

![Comparison of each parameter ($b_0$, $b_1$ and $b_2$) of equation 1 between the two study sites. A) Parameter $b_0$ denotes the intercept when t approaches a theoretical value of 0. B) Parameter $b_1$ denotes the scale parameter of the early decrease in ring density. C) Parameter $b_2$ denotes the rise in ring density at the end of the juvenile wood and at the beginning of the mature wood formation. The error bars represent standard deviation.](graph_table/summary_parameter)

@@

![The index of the amplitude of variation of the interannual density (index V), determined from equation 2. A) Average amplitude of the variation of the interannual density at the Asselin site. B) Average amplitude of variation in interannual density at Saint-Casimir site. The bars represent the standard deviation.](graph_table/IndexV)

@@

|Variables         |    R|P-value |
|:-----------------|----:|-------:|
|Density residus   | 0.57|8.7^-09^|
|Index V           | 0.08|0.43    |
|$b_0$             | 0.70|2.2^-16^|
|$b_1$             | 0.80|2.2^-16^|
|$b_2$             | 0.60|2.2^-16^|
Table: Spearman rank correlation coefficients and their P-values between the two study sites (Asselin and Saint-Casimir) of the density, the index of the amplitude of interannual variation of the density and parameters of the equation 1.

@@

![Individual inheritance of: Ring density, ring width, index of the interannual variation of density (Index_V), parameters ($b_0$, $b_1$ and $b_2$) of equation 1, earlywood density per ring (ew_density), earlywood percentage per ring (ew_percentage), earlywood width (ew_width), latewood density (lw_density), ring index interannual variation in latewood density (lw_index_V), latewood percent per ring (lw_percentage) and latewood width per ring (lw_width) for each of our two study sites. A) The traits of the entire ring per site, B) earlywood wood traits by ring and site, C) latewood traits by ring and site. The bars represent the standard error.](graph_table/heritability.pdf)
